Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-19 main.tex

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective 
  way to probe the electroweak sector of the Minimal Supersymmetric 
  Standard Model (MSSM). In this paper, we describe a search strategy  
  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles  at a 100 TeV 
  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP) via intermediate $Z$ and 
  SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
  $b$-quarks respectively: $\N_{2}\N_{3}
  \rightarrow (Z\N_1)(h\N_1)\rightarrow 
  bb\ell\ell+\N_1\N_1$. In addition, we examine 
  the potential for machine learning techniques to boost the power of 
  our searches. Using this analysis, Higgsinos up to 1.3 TeV can be 
  discovered for Binos  up to 0.9 TeV using 3000 fb$^{-1}$ of data,  
  Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially in the region where the mass difference between
Higgsino NLSP and LSP is smaller. \Shufang{Update the numbers.}
}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.   \Shufang{How about Br? What's the vcalue of M1 used?}\\
  \Shufang{Could you make the two plot same aspect ratios? Using plot digitizer.  Also, for ylabel in left panel, the tilde should not go above 0.  Just above $\chi$.  Is there way to change the xlabel of right panel to be $\mu$ instead of $|\mu|$?  Need to be consistent with the xlabels.}}
  \label{fig:xsection_plot}
\end{figure}

>>>>

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective 
  way to probe the electroweak sector of the Minimal Supersymmetric 
  Standard Model (MSSM). In this paper, we describe a search strategy  
  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV 
  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP) via intermediate $Z$ and 
  SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
  $b$-quarks respectively: $\N_{2}\N_{3}
  \rightarrow (Z\N_1)(h\N_1)\rightarrow 
  bb\ell\ell+\N_1\N_1$. In addition, we examine 
  the potential for machine learning techniques to boost the power of 
  our searches. Using this analysis, Higgsinos up to 1.3 TeV can be 
  discovered for Binos  up to 0.9 TeV using 3000 fb$^{-1}$ of data,  
  Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially in the region where the mass difference between
Higgsino NLSP and Bino LSP is smaller. \Shufang{Update the numbers.}
}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.   \Shufang{How about Br? What's the vcalue of M1 used?}\\
  \Shufang{Could you make the two plot same aspect ratios? Using plot digitizer.  Also, for ylabel in left panel, the tilde should not go above 0.  Just above $\chi$.  Is there way to change the xlabel of right panel to be $\mu$ instead of $|\mu|$?  Need to be consistent with the xlabels.}}
  \label{fig:xsection_plot}
\end{figure}
